# Computational Physiology & Mathematical Foundations

Building the mathematical and algorithmic prerequisites for autonomous control systems in medical automation. Currently focused on translating ordinary differential equations (ODEs) of metabolic dynamics into functional numerical simulations. As a Type 1 diabetic, I want to improve the systems used in medical devices to help a large group of people worldwide.

## Technical Vector
* **Computation:** Python (`SciPy`, `NumPy`, `Matplotlib`)
* **Mathematics:** Single-Variable Calculus (MIT 18.01 framework), Structural Logic (*Book of Proof*)
* **Domain Focus:** In-silico modeling of Type 1 Diabetes dynamics (e.g., Bergman Minimal Model)

## Active Vectors
* **`T1D-Control-Engine`**: Implementing and plotting physiological differential equations to simulate glucose-insulin feedback loops.
* **`math-foundations`**: Complete LaTeX type-ups of formal proofs and advanced calculus problem sets to verify structural logic.
* **`Polish Statistics Olympiad`**: Competing in the Polish Statistics Olympiad to improve my statistics, probability and combinatorics knowledge, while learning micro-, macro- and global economics.
* **`Polish Physics Olympiad`**: Competing in the Polish Physics Olympiad to use my newly gained calculus knowledge for real world problems.

## Future
* **`University`**: Planning to study Automation and Robotics (BSc) @ AGH Kraków 
* **`Coding`**: Moving to lower level languages like C++ and C, for microcontroller programming. 
* **`Mathematics`**: Completed MIT 18.01, 18.02, 18.03, 18.06 and Book of Proof.

---
"Trust the math, not the gut"
